Intrinsic Verification of Parsers and Formal Grammar Theory in Dependent Lambek Calculus

### 2025-03-25 paper/paper.tex
fix typo
fix issues with smallness, start smallness fig in appendix, fix a citation

\ifappendix
\appendix
\section{Syntax}
\begin{figure}
\begin{minipage}[t]{.35\textwidth}
  \begin{align*}
    \el\left(\Var\,M\right) B &= B\,M\\
    \el\left(\mathsf{K}\,A\right) B &= A\\
    \el\left(\bigoplus A\right) B &= \bigoplus_{y:Y}\el(A y)B\\
    \el\left(\bigamp A\right) B &= \bigamp_{y:Y}\el(A y)B\\
    \el\left(A \otimes A'\right) B &= \el(A)B \otimes \el(A')B
  \end{align*}
\end{minipage}%
\begin{minipage}[t]{.65\textwidth}
\begin{align*}
    \map\left(\Var\,M\right)\,f &= f\,M\\
    \map\left(\K\,A\right)\,f &= \lambda a. a\\
    \map\left(\bigoplus A\right)\,f &= \lambda a. \letin{\oplusinj y {a_y}}{a}{\oplusinj y {\map(A\,y)\,f\,a_y}}\\
    \map\left(\bigwith\,A\right)\,f &= \lambda a. \withlamb{y}{\map(A\,y)\,f\,(\withprj y a)}\\
    \map\left(A \otimes A'\right)\,f &= \lambda b. \letin{(a,a')}{b}{(\map(A)\,f\,a,\map(A')\,f\,a')}
  \end{align*}
\end{minipage}%
  \caption{Strictly positive functors functorial actions}
  \label{fig:spf-act}
\end{figure}

@@

In \cref{fig:spf-act}, we provide the functorial actions for the strictly
positive functors defined in \cref{fig:iilt}. We also include the full set of
rules for non-linear types in \cref{fig:full-non-linear-types}, and we provide
their judgmental equalities in \cref{fig:jdg-eq-nonlinear}. Finally,
\cref{fig:jdgeq} contains the judgmental equalities between linear terms in
\theoryabbv.

@@

  It is straightforward, but laborious to establish that all forms in
  the type theory that are parameterized by a non-linear context
  $\Gamma$ support the admissible actions of a substitution $\gamma
  \in \Subst(\Gamma',\Gamma)$ given in \cref{fig:non-linear-substitution,fig:substact}.
  %% Further, these all satisfy identity and composition equations M[\Gamma] = M and M[\gamma][\gamma'] = M[(\gamma \circ \gamma')]
\end{definition}

>>>>

\ifappendix
\appendix
\section{Syntax}
\begin{figure}
\begin{minipage}[t]{.35\textwidth}
  \begin{align*}
    \el\left(\Var\,M\right) B &= B\,M\\
    \el\left(\mathsf{K}\,A\right) B &= A\\
    \el\left(\bigoplus A\right) B &= \bigoplus_{y:Y}\el(A y)B\\
    \el\left(\bigamp A\right) B &= \bigamp_{y:Y}\el(A y)B\\
    \el\left(A \otimes A'\right) B &= \el(A)B \otimes \el(A')B
  \end{align*}
\end{minipage}%
\begin{minipage}[t]{.65\textwidth}
\begin{align*}
    \map\left(\Var\,M\right)\,f &= f\,M\\
    \map\left(\K\,A\right)\,f &= \lambda a. a\\
    \map\left(\bigoplus A\right)\,f &= \lambda a. \letin{\oplusinj y {a_y}}{a}{\oplusinj y {\map(A\,y)\,f\,a_y}}\\
    \map\left(\bigwith\,A\right)\,f &= \lambda a. \withlamb{y}{\map(A\,y)\,f\,(\withprj y a)}\\
    \map\left(A \otimes A'\right)\,f &= \lambda b. \letin{(a,a')}{b}{(\map(A)\,f\,a,\map(A')\,f\,a')}
  \end{align*}
\end{minipage}%
  \caption{Strictly positive functors functorial actions}
\end{figure}

@@

@@

  It is straightforward, but laborious to establish that all forms in
  the type theory that are parameterized by a non-linear context
  $\Gamma$ support the admissible actions of a substitution $\gamma
  \in \Subst(\Gamma',\Gamma)$ in \Cref{fig:non-linear-substitution}.
  %% Further, these all satisfy identity and composition equations M[\Gamma] = M and M[\gamma][\gamma'] = M[(\gamma \circ \gamma')]
\end{definition}
